---
title: "Barrera-Osorio et al, 2011"
author: "Dimitrios & Eva"
date: "`r Sys.Date()`"
output: 
  powerpoint_presentation:
    toc: true
    toc_depth: 1
    number_sections: true
    # theme: cerulean

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

# packages

library(knitrBootstrap)
library(dplyr)
library(haven)
library(table1)

```




# R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

# Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

# Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

# Slide with Plot

```{r pressure}
plot(pressure)
```

# Motivation

- Why is this research question relevant?
- What are the main hypotheses?


# Data sources

- Where does the data come from (country, time period, source)?
- What are the key variables?
- How are these measured?

# Method

- What are the assumptions of the method?
- Are these assumptions plausible in this example?
- Maybe: regression equation.




```{r data_prep, echo = FALSE}

# Importing STATA file

barrera <- read_dta("data/Public_Data_AEJApp_2010-0132.dta")

# Turning variables into factor variables. Following STATA convention.

barrera$i.s_teneviv <- as_factor(barrera$s_teneviv)
barrera$i.s_estcivil <- as_factor(barrera$s_estcivil)
barrera$i.s_estrato <- as_factor(barrera$s_estrato)
barrera$i.grade <- as_factor(barrera$grade)


# Filtering data in line with the following STATA code operations to reproduce table 3, columns 1-3:
# Dropping ineligible cases from Suba: Drop if suba == 1 and grade is < 9
# drop if suba == 1 & grade < 9; 
# The above seems to be a mistake in the STATA code: this should be grade < 6 instead of < 9. 
# Keeping only those who were selected for the survey:
# keep if survey_selected;
# Drop if they are in grade 11


# Filtered data

filtered_barrera <- barrera %>% filter(suba == 0, grade >= 6) %>%
  filter(survey_selected == 1) %>%
  filter(grade != 11)


# Filtering data in line with the following STATA code operations to reproduce table 3, columns 4-6:

filtered_barrera <- barrera %>% filter(suba == 0, grade >= 6) %>%
  filter(survey_selected == 1) %>%
  filter(grade != 11)

```





# Descriptive statistics

- Describe sample



```{r table1, echo = TRUE}

# Using n = 5,799 to get the sample actually used in our model. Variables selected based on Table 1

# House posessions - s_teneviv
# utilities - s_utilities
# durable goods - s_durables
# physical infrastructure - s_infraest_hh
# age - s_age_sorteo
# gender - s_sexo
# years of education - s_years
# single head - s_single
# Age of head - s_edadhead
# years of ed head - s_yrshead
# people in household - s_tpersona
# Member under 18 - s_num18
# estrato - s_estrato
# SISBEN - s_puntaje
# household income - s_ingtotal

table1(~ factor(s_teneviv)  | at_msamean, data=filtered_barrera)

```


```{r model1, echo = FALSE}


```


# Results

- Are these results plausible?
- How robust are the results to changing the sample?

```{r model1, echo = FALSE}

mod1 <- miceadds::lm.cluster(data = filtered_barrera, at_msamean ~ T1_treat + T2_treat,  cluster = "school_code")

summary(mod1)

```


# Conclusion

- Replication of a research paper: How do results compare to results of research paper?


```{r model1, echo = FALSE}


```



